---
title: "Statistical report for \n TECTO trial"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  word_document:
    toc: yes
    toc_depth: '2'
subtitle: Using simulated data
---

```{r setup, include=FALSE}
source("_scripts/_functions.R")
source("_scripts/_sim_data.R")
#source("_scripts/_import_data.R")
#source("_scripts/_data_handling.R")
#Kruskal wallis if not fullfilled.
```

\newpage
# Table 1 - Participant characteristics

```{r}
tbl_func(df,strat_var="group",vars=c("Age (years)","Gender","Nationality","Parental education level (ISCED)","Parental nationality",
                                     "Full-scale IQ","OCD-subtype",
                                     "Comorbidities|Depressive disorders","Comorbidities|Anxiety disorders",
                                     "Comorbidities|Adjustment disorders","Comorbidities|Eating disorders",
                                     "Comorbidities|Personality disorders","Comorbidities|Aspergers Syndrome",
                                     "Comorbidities|Hyperkinetic disorders","Comorbidities|Conduct disorders",
                                     "Comorbidities|Tics/Tourettes syndrome","Comorbidities|Elimination disorders"))

df_baseline <- df[,grepl("pt_id|group|_0", colnames(df))]
colnames(df_baseline) <- gsub("_0","",colnames(df_baseline))
tbl_func(df_baseline,strat_var="group",vars=c("CY-BOCS","KIDSCREEN","COIS-R","CGI-S","CGAS","TOCS"), Grepl=F, first.col.name = "Baseline psychopathology")

df_t3 <- df[grepl("group|FES|PSS_0|FAS-PR_0",colnames(df))]
colnames(df_t3) <- gsub("_0","",colnames(df_t3))
tbl_func(df_t3,strat_var="group",vars=c("FAS-PR","PSS","FES"), Grepl=T, first.col.name = "Family characteristics")

```

*The education-level from the parent with the highest education is used (using ISCED). For PSS, FES, and SRS the average of the parents who responded is presented.*

*CY-BOCS: Children’s Yale–Brown Obsessive Compulsive Scale; COIS-R: Child Obsessive-Compulsive Impact Scale-Revised; CGI-S: Clinical Global Impressions Severity; CGAS: Children’s Global Assessment Scale; TOCS: Toronto Obsessive-Compulsive Scale; FES: Family Environment Scale; PSS: Parental stress scale; FAS-PR: Family Accommodation Scale for Obsessive-Compulsive Disorder.*

\newpage
# Figure 1 - CONSORT flow diagram 

```{r, fig.height=7,fig.width=7.5, message=FALSE}
# consort.plot.R
# template for a CONSORT flow chart
# Feb 2017
library(diagram)
# dummy recruitment numbers
consort.assessed = 200
consort.excluded = 75
consort.declined = 50
consort.not.meet = 20
consort.other = 5
consort.randomised = consort.assessed - consort.excluded
allocate.control = allocate.treatment = 62
died.control = died.treatment = 1
lost.fu.control = died.control + 0
lost.fu.treatment = died.treatment + 0
excluded.control = 0
excluded.treatment = 0
analysed.treatment = allocate.treatment - excluded.treatment
analysed.control = allocate.control - excluded.control
pp.treatment = allocate.treatment - 5
pp.control = allocate.control - 5
# labels
b = c('Enrollment', 'Allocation', 'Follow-up', 'Analysis')
l1 = paste('Assessed for eligibility (n=', consort.assessed, ')', sep='') # numbers from above
l2 = paste('Excluded (n=', consort.excluded, ')\n',
           '•   Declined to participate (n=', consort.declined, ')\n',
           '•   Not meeting inclusion criteria (n=', consort.not.meet,')\n',
           '•   Other reasons (n=', consort.other, ')', sep='')
l3 = paste('Randomised (n=', consort.randomised,')', sep='')
l4 = paste('Allocated to control (n=', allocate.control ,')\n', sep='')
l5 = paste('Allocated to intervention (n=', allocate.treatment ,')\n',
           '• Received intervention (n=', allocate.treatment ,')\n', sep='')
l6 = paste('Lost to follow-up (n=', lost.fu.control, ')\n', # control lost to fu
           '•   Died (n=', died.control,')', sep='')
l7 = paste('Lost to follow-up (n=', lost.fu.treatment, ')\n', # treatment lost to fu
           '•   Died (n=', died.treatment,')', sep='')
l8 = paste('Analysed (n=', analysed.control, ')\n', 
           '•   Per protocol (n=', pp.control,')', sep='')
l9 = paste('Analysed (n=', analysed.treatment, ')\n', 
           '•   Per protocol (n=', pp.treatment,')', sep='')
labels = c(l1, l2, l3, l4, l5, l6, l7, l8, l9, b)
n.labels = length(labels)
### make data frame of box chars
frame = read.table(sep='\t', stringsAsFactors=F, skip=0, header=T, text='
i	x	y	box.col	box.type	box.prop	box.size
1	0.5	0.94	white	square	0.25	0.16
2	0.76	0.82	white	square	0.28	0.21
3	0.5	0.7	white	square	0.25	0.15
4	0.26	0.5	white	square	0.23	0.2
5	0.76	0.5	white	square	0.23	0.2
6	0.26	0.33	white	square	0.2	0.2
7	0.76	0.33	white	square	0.2	0.2
8	0.26	0.15	white	square	0.2	0.2
9	0.76	0.15	white	square	0.2	0.2
10	0.1	0.95	light blue	round	0.7	0.035
11	0.51	0.6	light blue	round	0.7	0.035
12	0.51	0.411	light blue	round	0.7	0.035
13	0.51	0.235	light blue	round	0.7	0.035')
pos = as.matrix(subset(frame, select=c(x, y)))
M = matrix(nrow = n.labels, ncol = n.labels, byrow = TRUE, data = 0)
M[3, 1] = "' '"
M[4, 3] = "' '"
M[5, 3] = "' '"
M[6, 4] = "' '"
M[7, 5] = "' '"
M[8, 6] = "' '"
M[9, 7] = "' '"
tcol = rep('black', n.labels)
to.blank = c(2,4:9)
tcol[to.blank] = 'transparent' # blank some boxes to add text as right aligned
#postscript('consort.flow.eps', width=7.5, height=7, horiz=F)
#tiff('consort.flow.tif', width=7.5, height=7, units='in', res=300, compression = 'lzw')
par(mai=c(0,0.04,0.04,0.04))
plotmat(M, pos = pos, name = labels, lwd = 1, shadow.size=0, curve=0,
        box.lwd = 2, cex.txt = 1, box.size = frame$box.size, box.col=frame$box.col,
        box.type = frame$box.type, box.prop = frame$box.prop, txt.col = tcol)
# add left-aligned text; -0.185 controls the horizontal indent
for (i in to.blank){
  text(x=pos[i,1] - 0.185, y=pos[i,2], adj=c(0,0.5), labels=labels[i]) # minus controls text position
}
# extra arrow to excluded
arrows(x0=0.5, x1=0.55, y0=0.82, length=0.12)




```

\newpage
# Figure 2 - Psychopathology and family burden

```{r, fig.height=8}

ggarrange(figScores(df,"CY-BOCS", lin_reg=T, parents="no") + theme(plot.background = element_rect(fill = "#f7f7ff",color=NA)),
          figScores(df,"KIDSCREEN", lin_reg=T, parents="yes") + theme(plot.background = element_rect(fill = "#fff7f7",color=NA)),
          figScores(df,"COIS-R", lin_reg=T, parents="yes"),
          figScores(df,"CGI-S", lin_reg=T, parents="no"),
          figScores(df,"CGI-I", lin_reg_simple=T, parents="no"),
          figScores(df,"CGAS", lin_reg=T, parents="no"),
          figScores(df,"TOCS", lin_reg=T, parents="yes"),
          figScores(df,"FAS-PR", lin_reg=T, parents="only"),
          figScores(df,"PSS", lin_reg=T, simple=F, parents="only"),
          g_legend(figScores(df,"KIDSCREEN", lin_reg=T, hide_legend=F, parents="yes")),
             ncol=1, heights=c(1,1,1,1,1,1,1,1,1,1,0.1)) +
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm"))  

```

*CY-BOCS: Children’s Yale–Brown Obsessive Compulsive Scale; COIS-R: Child Obsessive-Compulsive Impact Scale-Revised; CGI-S: Clinical Global Impressions Severity; CGI-I: Clinical Global Impressions Improvement; Children’s Global Assessment Scale; TOCS: Toronto Obsessive-Compulsive Scale; FAS-PR: Family Accommodation Scale for Obsessive-Compulsive Disorder; PSS: Parental stress scale.*

\newpage
# Figure 3 - Response status at 16 weeks

```{r fig.height=5}
df_bar <- data.frame(table(df$CBOCS_grup,df$group))
colnames(df_bar) <- c("severity","group","freq")
df_bar$perc[df_bar$group == "A"] <- df_bar$freq[df_bar$group == "A"]/sum(df_bar$freq[df_bar$group == "A"])
df_bar$perc[df_bar$group == "B"] <- df_bar$freq[df_bar$group == "B"]/sum(df_bar$freq[df_bar$group == "B"])

df_bar$x_axis[df_bar$group == "A"] <- 1
df_bar$x_axis[df_bar$group == "B"] <- 2

df_bar$cummu_sum[df_bar$group == "A"] <- cumsum(df_bar$perc[df_bar$group == "A"])
df_bar$cummu_sum[df_bar$group == "B"] <- cumsum(df_bar$perc[df_bar$group == "B"])

df_segment <- data.frame(cbind(df_bar$cummu_sum[df_bar$group == "A"],df_bar$cummu_sum[df_bar$group == "B"]))


df_bar$group <- as.character(df_bar$group)
df_bar$group[df_bar$group == "A"] <- 
paste0("A \n (n = ", sum(df_bar$freq[df_bar$group == "A"]), ")") 
df_bar$group[df_bar$group == "B"] <- 
paste0("B \n (n = ", sum(df_bar$freq[df_bar$group == "B"]), ")") 
df_bar$group <- as.factor(df_bar$group)

g1 <- ggplot(df_bar,aes(x=x_axis, fill=forcats::fct_rev(severity), color=forcats::fct_rev(severity), y=perc)) + 
  theme_minimal() +  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = c(1,2), labels=c(levels(df_bar$group))) +
  theme(legend.position = "top", legend.title = element_blank(),
        axis.title = element_blank(), panel.grid=element_blank()) +
  scale_fill_brewer(guide=guide_legend(reverse = TRUE), palette = "RdYlGn", direction=1) +
  scale_color_brewer(guide=guide_legend(reverse = TRUE), palette = "RdYlGn", direction=1)
 

g1 <-  g1 + geom_segment(aes(x=1.375,xend=1.625,y=0,yend=0), color="grey")

for(i in 1:nrow(df_segment)){
  g1 <-  g1 + geom_segment(aes_string(x=1.375,xend=1.625,y=df_segment[i,1],yend=df_segment[i,2]),color="grey")
}

g1 <- g1 + geom_bar(stat="identity", width=0.75) 


# Proportion of patients no longer meeting the diagnostic criteria for OCD, ICD-10 F.42 assesed with K-SADS-PL (82) at the end of the intervention (remission).

g2 <- ggplot(data=df_bar[df_bar$severity == "0-10 (Remitted)",], aes(x=group, y=perc)) + geom_bar(stat="identity", color="#000099", fill="#000099") + theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.title.y=element_blank()) + xlab("Remitted participants \n assessed using K-SADS-PL")
  

# Treatment response based on the definition of a reduction on the CY-BOCS at week 16 of at least 30% in intraindividual comparison with the score at week 0.  
df$Response <- as.numeric(as.character(df$Response))
test <- summarySE(df, measurevar="Response", groupvars="group",na.rm=T)
test$group <- as.character(test$group)
test$group[test$group == "A"] <- 
paste0("A \n (n = ", sum(test$N[test$group == "A"]), ")") 
test$group[test$group == "B"] <- 
paste0("B \n (n = ", sum(test$N[test$group == "B"]), ")") 
test$group <- as.factor(test$group)

g3 <- ggplot(data=test, aes(x=group, y=Response)) + geom_bar(stat="identity") + theme_minimal() +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.title.y=element_blank()) + xlab("Responders (with 30% reduction) \n assessed using CY-BOCS")
  



#ALL three figures
grid.arrange(g1 + watermarkGrob()
    ,g2 + watermarkGrob(),g3 + watermarkGrob(), layout_matrix=rbind(c(1,1),c(2,3)))

```

 

\newpage
# Figure 4 - Negative effects questionnaire 

```{r, fig.height=4}
fig_neq <- figScores(df,"NEQ", xminmax=c(3.5,16.5), simple=F, lin_reg_simple = T)
fig_burden <- ggplot(df, aes(x=group, y=`Negative effect burden`, color=group, fill=group)) + stat_summary(fun=mean, geom="bar", width=0.5) + 
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", width=0.25, color="black") + theme_minimal() +
  scale_color_hue(direction = -1, h.start=90) + scale_fill_hue(direction = -1, h.start=90) + 
  ylab("NEQ per week") + theme(axis.title.x = element_blank()) + 
  scale_color_manual(values=brewer.pal(n = 4, name = "Set1")[3:4]) + 
  scale_fill_manual(values=brewer.pal(n = 4, name = "Set1")[3:4])

ggarrange(fig_neq + watermarkGrob(), fig_burden + watermarkGrob(), ncol=1, common.legend=T, legend="bottom") + theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm"))



```


\newpage
# Supplemental Table 1 - Detailed comorbidities

```{r}
df_t3 <- df[grepl("group|F32.|F40.|F41.|F43.",colnames(df))]
tbl_func(df_t3,strat_var="group",vars=colnames(df_t3), Grepl=T)

```

\newpage
# Supplemental Table 2 - Psychopathology and family burden

*Numbers from Figure 2*

\newpage
# Supplemental Table 3 - Kidscreen-52

*Detailed scores from Kidscreen-52*

* Physical well-being
* Psychological well-being
* Moods and emotions
* Self-perception
* Autonomy
* Parent relation and home life
* Peers and social support
* School environment
* Social acceptance (bullying)
* Financial ressources

\newpage
# Supplemental Table 4 - SAE/SAR/SUSAR

*Raw data.*


\newpage
# Supplemental Timeline
This timeline will, together with the commits to the version control system, function as a log of the statistical process

* 14.04.2021 - The work on the statistical report with simulated data has been initiated.
* 30.04.2021 - First evaluation of presentation of data using simulated tools.
* 03.05.2021 - Second evaluation of the statistical report.
* 11.05.2021 - Third evaluation of the statistical report.
* 14.05.2021 - Fourth evaluation of the statistical report.
* 19.05.2021 - Fifth evaluation of the statistical report.
* 11.06.2021 - Corrections after sixth evaluation.
* 27.07.2021 - Correction after seventh evaluation.
* 09.03.2022 - Corresponds to the submitted version of the SAP

\newpage
# Supplemental Assumptions
The assumptions for regression models will be assessed using four figures, for each variable.

1. *Residuals vs Fitted*. Used to check the linear relationship assumptions. A horizontal line, without distinct patterns is an indication for a linear relationship, what is good.

2. *Normal Q-Q*. Used to examine whether the residuals are normally distributed. It’s good if residuals points follow the straight dashed line.

3. *Scale-Location* (or Spread-Location). Used to check the homogeneity of variance of the residuals (homoscedasticity). Horizontal line with equally spread points is a good indication of homoscedasticity.

4. *Residuals vs Leverage*. Used to identify influential cases, that is extreme values that might influence the regression results when included or excluded from the analysis.

## CY-BOCS (primary)

```{r fig.height = 4}
autoplot(lm(`CY-BOCS_16` ~ group + `CY-BOCS_0`, data=df)) + theme_minimal()
```

## KIDSCREEN-10 (secondary)

```{r fig.height = 4}
autoplot(lm(`KIDSCREEN_16` ~ group + `KIDSCREEN_0`, data=df)) + theme_minimal()
```

## NEQ (secondary)

```{r fig.height = 4}
autoplot(lm(`NEQ_16` ~ group, data=df)) + theme_minimal()
```

## COIS-R (exploratory)

```{r fig.height = 4}
autoplot(lm(`COIS-R_16` ~ group + `COIS-R_0`, data=df)) + theme_minimal()
```

## CGI-S (exploratory)

```{r fig.height = 4}
autoplot(lm(`CGI-S_16` ~ group + `CGI-S_0`, data=df)) + theme_minimal()
```

## CGI-I (exploratory)

```{r fig.height = 4}
autoplot(lm(`CGI-I_16` ~ group, data=df)) + theme_minimal()
```

## CGAS (exploratory)

```{r fig.height = 4}
autoplot(lm(`CGAS_16` ~ group + `CGAS_0`, data=df)) + theme_minimal()
```

## TOCS (exploratory)

```{r fig.height = 4}
autoplot(lm(`TOCS_16` ~ group + `TOCS_0`, data=df)) + theme_minimal()
```
